Fetch PMC Citation Info

### 2021-12-02 citation_fetching.Rmd
solved bug

get_cites <- function(PMCID) {
  mylink <- elink(uid=PMCID , dbFrom="pmc", dbTo = "pubmed")
  PMID <- mylink[1]
  CITES <- elink(uid = PMID , dbFrom = "pubmed"  , linkname = "pubmed_pubmed_citedin" )
  N_CITES <- length(CITES[1])
  PUBDATE <- get_pub_date(PMCID)
  return(c(PMCID,PMID,N_CITES,PUBDATE))
}

@@

## Get cites  and pu

```{r,reutils3}

@@

>>>>

get_cites <- function(PMCID) {
  mylink <- elink(uid=PMCID , dbFrom="pmc", dbTo = "pubmed")
  PMID <- mylink[1]
  CITES <- elink(uid = PMID , dbFrom = "pubmed"  , linkname = "pubmed_pubmed_citedin" )
  N_CITES <- length(CITES[1])
  #PUBDATE <- get_pub_date(PMCID)
  PUBDATE <- get_pub_date(PMID)
  return(c(PMCID,PMID,N_CITES,PUBDATE))
}

@@

## Get cites for small group

<!-- Now to get results for a few PMC IDs to test the functions are working OK. -->

```{r,test1}

@@

## Get cites for all

```{r,getcites}

x <- read.table("data/PMC_2019-analysis.tsv",sep="\t",header=TRUE)
head(x)
PMCIDS <- unique(x$Pubmed.Central.ID)
str(PMCIDS)

saveRDS(df,"cites_data.rds")
